appendix

### 2023-03-08 paper_comparison/appendix.Rmd

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~fct_relevel(education, "High School or below", "Diploma and Bachelor Degree", "Honours Degree", "Masters Degree")) +
  xlab("Age group") +
  ylab("Count")
```

@@

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~previous_experience) +
  xlab("Age group") +
  ylab("Count")
```

@@

```{r batch, fig.cap = "Boxplot of weighted propotion of detect for lineups over different data collection periods."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ggplot() +
  geom_boxplot(aes(x = factor(exp), y = prop_detect)) +
  facet_grid(~type) +
  scale_x_discrete(labels = c("I", "II", "III")) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

@@

```{r sensitive, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ inflated by 25% and deflated by 25%."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value)) %>%
  left_join(
vi_survey_upper %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_upper = first(p_value))) %>%
  left_join(
vi_survey_lower %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_lower = first(p_value))) %>%
  pivot_longer(p_value_upper:p_value_lower) %>%
  mutate(name = ifelse(name == "p_value_upper", "+25%", "-25%")) %>%
  ggplot() +
  geom_point(aes(p_value, value), alpha = 0.2) +
  geom_abline() +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~name) +
  ylab("Adjusted p-value") +
  xlab("p-value")

>>>>

```{r education, fig.cap = "\\label{fig:education}Education distribution of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~fct_relevel(education, "High School or below", "Diploma and Bachelor Degree", "Honours Degree", "Masters Degree")) +
  xlab("Age group") +
  ylab("Count")
```

@@

```{r experience, fig.cap = "\\label{fig:experience}Status of pervious experience of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~previous_experience) +
  xlab("Age group") +
  ylab("Count")
```

@@

```{r batch, fig.cap = "\\label{fig:batch}Boxplot of weighted propotion of detect for lineups over different data collection periods."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ggplot() +
  geom_boxplot(aes(x = factor(exp), y = prop_detect)) +
  facet_grid(~type) +
  scale_x_discrete(labels = c("I", "II", "III")) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

@@

```{r sensitive, fig.cap = "\\label{fig:sensitive}Change of $p$-values with $\\hat{\\alpha}$ inflated by 25% and deflated by 25%."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value)) %>%
  left_join(
vi_survey_upper %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_upper = first(p_value))) %>%
  left_join(
vi_survey_lower %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_lower = first(p_value))) %>%
  pivot_longer(p_value_upper:p_value_lower) %>%
  mutate(name = ifelse(name == "p_value_upper", "+25%", "-25%")) %>%
  ggplot() +
  geom_point(aes(p_value, value), alpha = 0.2) +
  geom_abline() +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~name) +
  ylab("Adjusted p-value") +
  xlab("p-value")
